On the means, costs, and system-level impacts of the 24/7 carbon-free energy procurement

### 2023-10-15 manuscript/sections/supplementary_2.tex
si: add background system assumptions

%S2: Background system assumptions
In all the modelled countries, renewable generation must meet the political targets as defined in the NECPs or by more recent national policy targets (such as the Easter package in Germany), see Table 1.

>>>>

%S2: Background system assumptions

The model performs \textit{a perfect-foresight optimisation} of investment and power dispatch decisions to meet electricity demand of the 24/7 consumers, as well as the demand of other consumers in the European electricity system for 2025 or 2030.

In all the modelled countries, renewable generation \textit{must meet the political targets} as defined in the \gls{necp}s or by more recent national policy targets (such as the Easter package in Germany). In countries that not have a target for 2025, a linear increase from targets between 2020 and 2030 is assumed. The assumed renewable targets are available in the config file of the scientific workflow \cite{github-247CFEpaper}.

We assume 2013 to be a representative climate year for renewable in-feed. The renewable feed-in profiles are computed with the atlite package \cite{atlite-github}.

The country demand profiles for 2025 and 2030 are assumed to be the same as in 2013. Time-series data for electricity demand is based on the Open Power System Data project \cite{OPSD}.

The existing power plant fleet data is based on the powerplantmatching package \cite{Powerplantmatching-github}. We consider national policies and decommissioning plans for coal and nuclear power plants based on data from the \enquote{beyondfossilfuels.org} and the \enquote{world-nuclear.org} projects \cite{FossilFuels, WorldNuclearAssociation}.

We assume price for EU ETS allowances to be 80~\euro/t\co and 130~\euro/t\co  for 2025 and 2030, accordingly. 
The price for natural gas is assumed to be 35~\euro/MWh.
